We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2017-11-04 paper/paper.tex
paper

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellites asphericity ]{We are not the 99 percent: quantifying
  asphericity in the Local Group satellites' distributions}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellites distribution asphericity]{We are not the 99 percent: quantifying
  asphericity in the distribution of Local Group satellites}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\section{Conclusions}

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the Local Group.
The method uses as a basic condition the spherical randomization of
satellite positions (observed or simulated). 
The scalars describing the satellite distribution in each galaxy are
then normalized to the mean value and standard deviation in the
randomized samples.

In observations we limit our analysis to the 11 brightest satellites 
in the Milky Way and Andromeda. 
For numerical data we use the Illustris-1 and the ELVIS simulations.

We find that the deviation from aesphericity in the LG is only
expected in $1\pm3$ pairs out of a sample of $2000$ isolated pairs. 
This places the LG as a $3\sigma$ outlier. 
The weight to explain this atypical result is not distributed equally
between the MW and M31. While M31 presents a fully typical asphericity
in the expectations from LCDM, the MW shows aspherical deviations in
plane width and the major-to-minor axis ratio highly atypical in the
framework of LCDM. 
We estimate that with the M31 $XX$ out of $2000$ pairs show normalized
characteristics larget r equal than M31, while this number drops to 
$XX$ for the MW.
